### 2011-08-27 doc/theses/vitasek/chapter-4-experiments.tex
Thesis: in progress.

TODO just table (mean, variance), no chart + interpretation

@@

TODO graph + interpretation

@@

TODO interpretation. Graph should has its Y axis in log, stress this fact in the text too

@@

@@

TODO graphs (files with similar behavior together) + interpretation.

@@

TODO compare all CHs - limit GLPK to ~ 1 second
TODO pool size 10 where applicable

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Quad Core \\
  Input data        & all official test data sets \\
  Iterations        & 20 \\
  Pool size         & 10 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

>>>>

\begin{table}
  \caption{Grammar and Model Creation Times}
  \bigskip
  \label{table-experiments-grammar-model-timing}
  \centering
  \begin{tabular}{l || l | l || l | l || l | l}
    Data set & GE avg [ms] & GE stdev & MC avg [ms] & MC stdev & Tot avg [ms] & Tot stdev \\
    \hline
    \dataset{OVA1}     & < 10 & - & < 10 & - < 10 & - \\
    \dataset{OVA2}     & < 10 & - & < 10 & - < 10 & - \\
    \dataset{OVA3}     & 42.94 & 19.8509 & 60.92 & 27.0848 & 103.86	& 31.6911 \\
    \dataset{XMA-c}    & 140.32 &	33.2618 &	90.24 &	45.8803 & 230.56 & 56.2633 \\
	\dataset{XMA-p}    & 7518.82 &	922.8882 &	10135.46 &	502.8997 & 17654.28	& 1353.8794 \\
	\dataset{XMD}      & 979.18 &	307.1760 &	563.04 & 341.4697 & 1542.22	& 134.6883 \\
	\dataset{MSH}      & 570.24 &	167.1119 &	225.48 &	90.6775 & 795.72 & 161.8340 \\ 
	\dataset{NTH}      & 328.36 & 118.3766 &	1074.9 &	155.5604 & 1403.26 & 137.8695 \\
	\dataset{100-100}  & < 10 & - & < 10 & - & < 10 & - \\
	\dataset{100-200}  & < 10 & - & < 10 & - & < 10 & - \\
	\dataset{100-1000} & 18.34 & 10.2372 & 18.84 & 1.0373 & 37.18 & 9.9338 \\
	\dataset{0-0}      & < 10 & - & < 10 & - & < 10 & - \\
	\dataset{10-5}     & < 10 & - & < 10 & - & < 10 & - \\
	\dataset{20-20}    & < 10 & - & < 10 & - & < 10 & - \\
	\dataset{30-45}    & < 10 & - & < 10 & - & < 10 & - \\
	\dataset{40-80}    & < 10 & - & < 10 & - & < 10 & - \\
	\dataset{50-125}   & < 10 & - & < 10 & - & < 10 & - \\
	\dataset{60-180}   & < 10 & - & < 10 & - & < 10 & - \\
	\dataset{70-245}   & < 10 & - & < 10 & - & < 10 & - \\
	\dataset{80-320}   & < 10 & - & < 10 & - & 12.48 & 8.3574 \\
	\dataset{90-405}   & < 10 & - & < 10 & - & 15.88 & 10.3778 \\
	\dataset{100-500}  & < 10 & - & < 10 & - & 18.74 &	8.8889 \\
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{GLPK Interface Times}
  \bigskip
  \label{table-experiments-glpk-timing}
  \centering
  \begin{tabular}{l || l | l || l | l || l | l}
	Data set & IC avg [ms] & IC stdev & OP avg [ms] & OP stdev & Tot avg [ms] & Tot stdev \\
	\hline
	\dataset{OVA1} & 36.46 & 66.8517 & 49.8 & 114.0687 & 86.26 & 150.1044 \\
	\dataset{OVA2} & 39.52 & 75.8210 & 48.8 & 102.4484 & 88.32 & 154.9596 \\
	\dataset{OVA3} & 34.1 & 74.1838 & 38.62 & 89.3772 & 72.72 & 134.7295 \\
	\dataset{XMA-c} & 40.88 & 88.6632 & 33.84 & 65.8636 & 74.72 & 127.7338 \\
	\dataset{XMA-p} & 36.54 & 70.7436 & 49.24 & 101.2412 & 85.78 & 145.2092 \\
	\dataset{XMD} & 37.98 & 69.2719 & 32.88 & 70.2173 & 70.86 & 114.6692 \\
	\dataset{MSH} & 40.42 & 91.9885 & 36.52 & 72.1018 & 76.94 & 138.6198 \\
	\dataset{NTH} & 36.02 & 66.3403 & 38.06 & 88.8244 & 74.08 & 128.9974 \\
	\dataset{100-100} & 46.5 & 103.3929 & 46.92 & 89.7049 & 93.42 & 158.7267 \\
	\dataset{100-200} & 42.34 & 96.1204 & 38.22 & 90.0284 & 80.56 & 152.6534 \\
	\dataset{100-1000} & 32.92 & 64.4534 & 42.1 & 89.4546 & 75.02 & 127.8541 \\
	\dataset{0-0} & 46.8 & 123.5183 & 46.92 & 102.2601 & 93.72 & 181.5228 \\
	\dataset{10-5} & 40.06 & 75.7370 & 40.1 & 72.4851 & 80.16 & 126.7135 \\
	\dataset{20-20} & 33.72 & 70.7263 & 34.1 & 66.2781 & 67.82 & 116.3783 \\
	\dataset{30-45} & 38.26 & 71.7549 & 45.94 & 110.1284 & 84.2 & 155.7594 \\
	\dataset{40-80} & 37.06 & 67.0024 & 49.26 & 106.3185 & 86.32 & 144.9918 \\
	\dataset{50-125} & 50.44 & 101.9162 & 84.76 & 364.7350 & 135.2 & 378.7835 \\
	\dataset{60-180} & 38.38 & 89.3379 & 42.54 & 94.3742 & 80.92 & 149.6049 \\
	\dataset{70-245} & 41.5 & 93.2951 & 40.3 & 93.4858 & 81.8 & 149.6797 \\
	\dataset{80-320} & 51.92 & 121.9812 & 47.98 & 96.0904 & 99.9 & 171.4617 \\
	\dataset{90-405} & 40.5 & 91.5373 & 36.46 & 88.5099 & 76.96 & 144.2890 \\
	\dataset{100-500} & 37.82 & 85.7571 & 43.4 & 90.3257 & 81.22 & 141.9103 \\
  \end{tabular}
\end{table}

TODO interpretation: it is interesting that even though $|V|$ and $|E|$ are increasing, the times remain almost the same. This probably means that the most of the time is spent in I/O.

@@

TODO interpretation. Graph has its Y axis in log, stress this fact in the text too

@@

TODO pie chart of all relevant times: grammar, model, GLPK in, GLPK, GLPK out

@@

TODO repair outliers in these 2 graphs

\begin{figure}
  \caption{Random vs. Fuzzy vs. FIDAX - Quality}
  \label{image-experiment-random-fuzzy-fidax-quality}
  \centering
    \includegraphics[width=\textwidth]{images/experiments/random-fuzzy-fidax-quality}
\end{figure}

\begin{figure}
  \caption{Random vs. Fuzzy vs. FIDAX - Time}
  \label{image-experiment-random-fuzzy-fidax-time}
  \centering
    \includegraphics[width=\textwidth]{images/experiments/random-fuzzy-fidax-time}
\end{figure}

TODO interpretation - Fuzzy consistently wins, but takes the longest time by far. Random is better than FIDAX in artificial as well as some real data.

@@

TODO compare all CHs - limit GLPK to 1 second
TODO pool size 10 where applicable

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Quad Core \\
  Input data        & all official test data sets \\
  Iterations        & 50 \\
  Pool size         & 10 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}
